---
title: "Assingment: Rmarkdown & Leaflet"
subtitle: "Data Science: Developing Data Products"
author: "Yellow Duck"
date: "September 4, 2019"
output: html_document
---
******

## Intructions 

Create a web page using **R Markdown** that features a map created with **Leaflet**. Host your webpage on either GitHub Pages, **RPubs**, or NeoCities.  
Your webpage must contain:  

* date that you created the document, and 
* map created with Leaflet.  

## Submission  

If it's Friday then we are in Ireland!


```{r one, eval = TRUE, echo = FALSE}
library(leaflet)
```

Where we will vist seven oldest pubs in the country ... at least based on [The Oldest Pubs in Ireland](https://tbexcon.com/blog/oldest-pubs-in-ireland/)! 


```{r two, eval = TRUE, echo = FALSE}
pubByYear = data.frame(
  long  = c(-6.216,-5.923, -8.735, -5.537, -7.253, -6.276, -7.942), 
  lat   = c(53.223, 54.601, 51.746, 54.38, 52.653, 53.344, 53.422), 
  year  = c(1798, 1711, 1698, 1611, 1263, 1198, 900), 
  name  = c("Johnny Fox’s Pub, Glencullen, Dublin", "McHugh’s Bar, Belfast", "Gateway Bar, Cork City", "Grace Neill’s, Donaghadee, Down", "Kyteler’s Inn, Kilkenny", "Brazen Head, Dublin", "Sean’s Bar, Athlone" ))

leaflet(data = pubByYear) %>% addTiles() %>%
  addMarkers(~long, ~lat, popup = ~as.character(year), label = ~as.character(name),  clusterOptions = markerClusterOptions())
```


Let's start with Johnny Fox's Pub located 23.9km drive from Dublin Airport.  

```{r three, eval = TRUE, echo = FALSE}
leaflet() %>%
  addTiles %>%
  setView(lng = -6.26, lat = 53.35, zoom = 10) %>%
  addMarkers(lng = -6.216, lat = 53.223, popup = "Johnny Fox’s Pub") %>% 
  addMarkers(lng = -6.3, lat = 53.43, popup = "Dublin Airport")
```

